Goes Here

### 2012-08-01 paper.tex
figure for probability of loaded die

 \teaser{
   \begin{subfigure}[b]{0.3\textwidth}
	\centering
    	\includegraphics[width=0.6\textwidth]{figure/bunny_orig.png}
      	\caption{}
        \label{teaser:original}
        \end{subfigure}
        ~ 
        \begin{subfigure}[b]{0.18\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print1.jpg}
                \caption{}
                \label{teaser:ours}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print2.jpg}
                \caption{}
                \label{teaser:makerbot}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.18\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print3.jpg}
                \caption{}
                \label{teaser:objet}
        \end{subfigure}
        \caption{A textured mesh printed with different types of 3D printers.
        	(a)original model.(b)printed with our printer.(c)makerbot.
        	(d)objet}\label{teaser}
 }

@@

is usually high-dimensional. For example, when the printing

@@

has $N^M$ dimensions. To overcome this problem, we decompose the search

@@

@@

such as simulated annealing, genetic algorithms and
Markov Chain Monte Carlo methods, as well as custom optimization algorithms implemented

@@

Code examples:
To generate textured model:
\begin{verbatim}
Manager manager;
manager.loadMaterialLib("material_file");
manager.setGenerator(
  new HeightFieldGenerator());
manager.setSimulator(colorSimulator());
manager.setMetric(someColorMetric());
manager.setOptimizer(
  simulatedAnealing);
  //or e.g. gradientDescent
Objective obj;
Scene scene;
TexturedShape shape("filename");
TexturedShape goal("filename1");
scene.addShape(shape);
obj.setScene(scene);
obj.setGoal(goal);
manager.addObjective(obj);
\end{verbatim}

@@

\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
A figure showing a material with a particular
look and deformation properties is shown in Figure~\ref{fig:deform}

@@

We expand gamut of printable colors by stacking translucent materials. We then applied
dithering with our expanded colors.
\subsection{New Examples for Mechanical Properties}
Ball bounce to certain height.

@@

A loaded die as shown in Figure~\ref{fig:die}. 
\begin{figure}
	\centering
 	\includegraphics[width=0.25\textwidth]{figure/die.png}
\caption{A printed loaded die}
\label{fig:die}
\end{figure}
It has a certain probability to land on "1".
A table of probability distribution of landing on each side
is shown in Table~\ref{tab:dice}.

@@

A plot of simulated probability of landing on "1" after each iteration.

@@

\section{Possible Extension}
UI to specify input deformation.
\section{Conclusion}
\section*{Acknowledgements}

>>>>

 \teaser{
   \begin{subfigure}[b]{0.3\textwidth}
	\centering
    	\includegraphics[width=0.6\textwidth]{figure/bunny_orig.png}
      	\caption{}
        \label{teaser:original}
        \end{subfigure}
        ~ 
        \begin{subfigure}[b]{0.18\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print1.jpg}
                \caption{}
                \label{teaser:ours}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print2.jpg}
                \caption{}
                \label{teaser:makerbot}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.18\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print3.jpg}
                \caption{}
                \label{teaser:objet}
        \end{subfigure}
        \caption{A textured mesh printed with different types of 3D printers.
        	(a)original model.(b)printed with our printer.(c)makerbot.
        	(d)objet}\label{teaser}
	\label{fig:texture}
 }

@@

is usually intractable. For example, when the printing

@@

contains $N^M$ choices. To overcome this problem, we decompose the search

@@

In this paper, all reduction models are manually specified by us.

@@

such as simulated annealing, variational inference and
Markov Chain Monte Carlo methods,
as well as custom optimization algorithms implemented

@@

We provide a built-in library that handles common tasks such as assigning texture,
simulating deformation, and optimizing for a stacking.
A casual user mostly make function calls to an existing 
manager to pass data and to run the optimization.
More advanced user can configure the manager to achieve more specific requirements.
For example, he can swap out an existing optimization module to achieve a better accuracy or 
a faster speed.
A professional user can implement more modules when he wants to deal with new
material properties that are not handled by our built-in library. In that case,
he needs to know what value the new property is in print materials, he needs to know
how to simulate for the new property, and how to measure error of the new property.

In below, we provide code snippets that handles three common tasks
that we expect a moderately advanced user would write.

Code examples:
To generate textured model:
\begin{verbatim}
Manager manager;
manager.loadMaterialLib("material_file");
manager.setGenerator(
  new HeightFieldGenerator());
manager.setSimulator(colorSimulator());
manager.setMetric(someColorMetric());
manager.setOptimizer(
  simulatedAnealing);
  //or e.g. gradientDescent
Objective obj;
Scene scene;
TexturedShape shape("filename");
TexturedShape goal("filename1");
scene.addShape(shape);
obj.setScene(scene);
obj.setGoal(goal);
manager.addObjective(obj);
\end{verbatim}

@@

\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
A material with a particular
look and deformation properties is shown in Figure~\ref{fig:deform}

@@

We expand gamut of printable colors by stacking translucent materials. We then applied
dithering with our expanded colors.
Results are shown in Figure~\ref{fig:texture}
\subsection{New Examples for Mechanical Properties}
Ball bounce to certain height.

@@

A loaded die as shown in Figure~\ref{fig:die}. This example is interesting because
a local change will have some global effect.
\begin{figure}
	\centering
 	\includegraphics[width=0.25\textwidth]{figure/die.png}
\caption{A printed loaded die}
\label{fig:die}
\end{figure}
It has a certain probability to land on "1".
A table of probability distribution of landing on each side
is shown in Table~\ref{tab:dice}.

@@

A plot of simulated probability of landing on "1" after each iteration
is shown in Figure~\ref{fig:dieErr}.

\begin{figure}
	\centering
 	\includegraphics[width=0.3\textwidth]{figure/die.pdf}
\caption{Probability of die landing on 1 after each iteration.}
\label{fig:dieErr}
\end{figure}

@@

More ideas:
balancing bird with texture.
\section{Possible Extension}
UI to specify input deformation.
\section{Conclusion}
\section*{Acknowledgements}
